Reformulating phylogenetic models to improve flexibility and speed

### 2018-05-23 main.tex
bmb changes

In this paper, we will propose an alternative formulation of phylogenetic generalized linear mixed models that is mathematically equivalent to previous approaches.
However, our new formulation is more flexible and can be easily extended along with the features of mixed model such as multiple observational designs, phylogenetic random-slopes models, random interactions \ml{why not? we are already using this for the alternative formulation of nested RE} and nested random effect models.
We will compare our technique with existing methods to show robustness and efficiency via simulations and data.
We end by discussing opportunities and practicalities of our method and considering the state of art for this area of research.

>>>>

In this paper, we will propose an alternative formulation of phylogenetic generalized linear mixed models that is mathematically equivalent to previous approaches.
However, our new formulation is more flexible and can be easily extended along with the features of mixed model such as multiple observational designs, phylogenetic random-slopes models, and multiple (nested or crossed) random effects.
We will compare our technique with existing methods to show robustness and efficiency via simulations and data.
We end by discussing opportunities and practicalities of our method and considering the state of art for this area of research.
